---
title: "Final Project Tables"
output: pdf_document
---

```{r  results="hide", echo=FALSE, message=FALSE, warning=FALSE}
library(data.table)
library(MASS)

d = fread('~/MIDS/W241/final project/data.csv')

# data manipulation
d[city==1, population := 2.1]
d[city==2, population := 7]
d[city==3, population := 3.25]
d[city==4, population := 8.4]
d[city==5, population := 18.55]

d$avgoffer = as.numeric(d$avgoffer)

d$city = factor(d$city)

# standard error of the mean function
sem <- function(x) sqrt(var(x) / length(x))
```

```{r results="hide", echo=FALSE, message=FALSE, warning=FALSE}
d[,sum(treatment),by=city]                  # treatment/control split by city (50% for each city by design)
table(d$city, d$author)                     # author distribution by city (random)
d[,sum(treatment),by=day]                   # treatment/control split by day (random)
table(d$day, d$author)                      # author distribution by day (random)
```

| | City 1 | City 2 | City 3 | City 4 | City 5 |
| ---: | :---: | :---: | :---: | :---: | :---: |
| Population (millions): | 2.1 | 7 | 3.25 | 8.4 | 18.55 |
| Treatment Ads: | 10 | 10 | 10 | 10 | 10 |
| Control Ads: | 10 | 10 | 10 | 10 | 10 |
| Author 1 Ads: | 3 | 2 | 3 | 7 | 5 |
| Author 2 Ads: | 5 | 7 | 3 | 3 | 2 |
| Author 3 Ads: | 7 | 5 | 2 | 3 | 3 |
| Author 4 Ads: | 2 | 3 | 7 | 1 | 7 |
| Author 5 Ads: | 3 | 3 | 5 | 6 | 3 |

| | Day 1 | Day 2 | Day 3 | Day 4 |
| ---: | :---: | :---: | :---: | :---: |
| Treatment Ads: | 15 | 11 | 9 | 15 |
| Control Ads: | 10 | 14 | 16 | 10 |
| Author 1 Ads: | 5 | 8 | 3 | 4 |
| Author 2 Ads: | 3 | 4 | 4 | 9 |
| Author 3 Ads: | 8 | 6 | 2 | 4 |
| Author 4 Ads: | 6 | 4 | 7 | 3 |
| Author 5 Ads: | 3 | 3 | 9 | 5 |



```{r echo=FALSE}
# mean response count
rtotal = d[,.(m = mean(rtotal), se = sem(rtotal)),by=treatment]
rtotal.m.1 = rtotal[treatment==1]$m
rtotal.se.1 = format(rtotal[treatment==1]$se, digits=2)
rtotal.m.0 = rtotal[treatment==0]$m
rtotal.se.0 = format(rtotal[treatment==0]$se, digits=2)

# mean offer count
roffer = d[,.(m = mean(roffer), se = sem(roffer)),by=treatment]
roffer.m.1 = roffer[treatment==1]$m
roffer.se.1 = format(roffer[treatment==1]$se, digits=2)
roffer.m.0 = roffer[treatment==0]$m
roffer.se.0 = format(roffer[treatment==0]$se, digits=2)

# mean offer amount (this is the average offer amount, not average of the averages...not using it)
offer.mean.1 = sum(d[treatment==1,avgoffer*roffer], na.rm=T) / sum(d[treatment==1,roffer])
offer.mean.0 = sum(d[treatment==0,avgoffer*roffer], na.rm=T) / sum(d[treatment==0,roffer])

# here is the average of the averages
avg = d[!is.na(avgoffer),.(m = mean(avgoffer), se = sem(roffer)),by=treatment]
avg.m.1 = round(avg[treatment==1]$m, 2)
avg.se.1 = round(avg[treatment==1]$se, 2)
avg.m.0 = round(avg[treatment==0]$m, 2)
avg.se.0 = round(avg[treatment==0]$se, 2)

```

| | Treatment | Control |
| ---: | :---: | :---: |
| Mean Response Count: | `r rtotal.m.1` (`r  rtotal.se.1`) | `r rtotal.m.0` (`r rtotal.se.0`) |
| Mean Offer Count: | `r roffer.m.1` (`r  roffer.se.1`) | `r roffer.m.0` (`r roffer.se.0`) |
| Mean Mean Offer: | `r avg.m.1` (`r  avg.se.1`) | `r avg.m.0` (`r avg.se.0`) |
