---
title: "Final Project Tables"
output: html_document
---

```{r  results="hide", echo=FALSE, message=FALSE, warning=FALSE}
library(data.table)
library(MASS)
library(stargazer)

d = fread('/Users/koza/Documents/UCBerkeley/241/w241Project/R/daniel_data.csv')

# data manipulation
d[city==1, population := 2.1]
d[city==2, population := 7]
d[city==3, population := 3.25]
d[city==4, population := 8.4]
d[city==5, population := 18.55]

d$avgoffer = as.numeric(d$avgoffer)

d$city = factor(d$city)

# standard error of the mean function
sem <- function(x) sqrt(var(x) / length(x))
```

```{r results="hide", echo=FALSE, message=FALSE, warning=FALSE}
# Descriptive Statistics: Randomization
d[,sum(treatment),by=city]                  # treatment/control split by city (50% for each city by design)
table(d$city, d$author)                     # author distribution by city (random)
d[,sum(treatment),by=day]                   # treatment/control split by day (random)
table(d$day, d$author)                      # author distribution by day (random)
```

| | City 1 | City 2 | City 3 | City 4 | City 5 |
| ---: | :---: | :---: | :---: | :---: | :---: |
| Population (millions): | 2.1 | 7 | 3.25 | 8.4 | 18.55 |
| Treatment Ads: | 10 | 10 | 10 | 10 | 10 |
| Control Ads: | 10 | 10 | 10 | 10 | 10 |
| Author 1 Ads: | 3 | 2 | 3 | 7 | 5 |
| Author 2 Ads: | 5 | 7 | 3 | 3 | 2 |
| Author 3 Ads: | 7 | 5 | 2 | 3 | 3 |
| Author 4 Ads: | 2 | 3 | 7 | 1 | 7 |
| Author 5 Ads: | 3 | 3 | 5 | 6 | 3 |

| | Day 1 | Day 2 | Day 3 | Day 4 |
| ---: | :---: | :---: | :---: | :---: |
| Treatment Ads: | 15 | 11 | 9 | 15 |
| Control Ads: | 10 | 14 | 16 | 10 |
| Author 1 Ads: | 5 | 8 | 3 | 4 |
| Author 2 Ads: | 3 | 4 | 4 | 9 |
| Author 3 Ads: | 8 | 6 | 2 | 4 |
| Author 4 Ads: | 6 | 4 | 7 | 3 |
| Author 5 Ads: | 3 | 3 | 9 | 5 |



```{r echo=FALSE}
# Descriptive Statistics: Outcomes

# mean response count
rtotal = d[,.(m = mean(rtotal), se = sem(rtotal)),by=treatment]
rtotal.m.1 = rtotal[treatment==1]$m
rtotal.se.1 = format(rtotal[treatment==1]$se, digits=2)
rtotal.m.0 = rtotal[treatment==0]$m
rtotal.se.0 = format(rtotal[treatment==0]$se, digits=2)

# mean offer count
roffer = d[,.(m = mean(roffer), se = sem(roffer)),by=treatment]
roffer.m.1 = roffer[treatment==1]$m
roffer.se.1 = format(roffer[treatment==1]$se, digits=2)
roffer.m.0 = roffer[treatment==0]$m
roffer.se.0 = format(roffer[treatment==0]$se, digits=2)

# mean offer amount (this is the average offer amount, not average of the averages...not using it)
offer.mean.1 = sum(d[treatment==1,avgoffer*roffer], na.rm=T) / sum(d[treatment==1,roffer])
offer.mean.0 = sum(d[treatment==0,avgoffer*roffer], na.rm=T) / sum(d[treatment==0,roffer])

# here is the average of the averages
avg = d[!is.na(avgoffer),.(m = mean(avgoffer), se = sem(roffer)),by=treatment]
avg.m.1 = round(avg[treatment==1]$m, 2)
avg.se.1 = round(avg[treatment==1]$se, 2)
avg.m.0 = round(avg[treatment==0]$m, 2)
avg.se.0 = round(avg[treatment==0]$se, 2)

```

| | Treatment | Control |
| ---: | :---: | :---: |
| Mean Response Count: | `r rtotal.m.1` (`r  rtotal.se.1`) | `r rtotal.m.0` (`r rtotal.se.0`) |
| Mean Offer Count: | `r roffer.m.1` (`r  roffer.se.1`) | `r roffer.m.0` (`r roffer.se.0`) |
| Mean Mean Offer: | `r avg.m.1` (`r  avg.se.1`) | `r avg.m.0` (`r avg.se.0`) |

```{r echo=FALSE, message=FALSE, warning=FALSE}
# rtotal Regression
mod1.ols = lm(rtotal ~ treatment, data=d)
mod2.ols = lm(rtotal ~ treatment + factor(pairid), data=d)
mod3.ols = lm(rtotal ~ treatment + factor(pairid) + population, data=d)
mod4.ols = lm(rtotal ~ treatment + factor(pairid) + population + factor(city) + factor(day) + author, data=d)
mod1.pois = glm(rtotal ~ treatment, data=d, family = "poisson")
mod2.pois = glm(rtotal ~ treatment + factor(pairid), data=d, family = "poisson")
mod3.pois = glm(rtotal ~ treatment + factor(pairid) + population, data=d, family = "poisson")
mod4.pois = glm(rtotal ~ treatment + factor(pairid) + population + factor(city) + factor(day) + author, data=d, family = "poisson")

# We're using poisson because the data are 0-heavy,
# positively skewed count (non-negative) data. Histogram shows this
# hist(d$rtotal, breaks=30)

# the pretty version:
hist(d$rtotal, col="honeydew4", 
     border="white", 
     main=paste("Response Count"), 
     cex.main=2,
     font.main=1,
     xlab="Number of responses", 
     ylab="Frequency",
     col.main="gray20",
     col.lab="gray20",
     cex.axis=1.5,
     cex.lab=1.5,
     lwd=.5,
     breaks=30, 
     xlim=c(0,30)
     )
#axis(1,col="gray100")
#axis(2,col="gray100")



# qqplot shows the residual distribution from OLS regression (i.e. also illustrates that OLS
# is inappropriate)
ols.stdres = rstandard(mod2.ols)
qqnorm(ols.stdres, 
       ylab="Standardized Residuals", 
       xlab="Normal Scores",
       col.main="gray20",
       col.lab="gray20",
       col.axis="gray20",
       lwd=.5,
       font.main=1,
       cex.main=2,
       cex.axis=1.5,
       cex.lab=1.5,
       main="Residual distribution"
       ) 
qqline(ols.stdres)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Both OLS and poisson together. Not sure if this is useful
#stargazer(mod1.ols, mod2.ols, mod3.ols, mod4.ols, mod1.pois, mod2.pois, mod3.pois, mod4.pois,
#          omit=c("^factor.*", "^author.*"), 
#          add.lines = list(
#            c("Pair Fixed effects?", "No", "Yes", "Yes", "Yes", "No", "Yes", "Yes", "Yes"),
#            c("Day Fixed effects?", "No", "No", "No", "Yes", "No", "No", "No", "Yes"),
#            c("Author Fixed effects?", "No", "No", "No", "Yes", "No", "No", "No", "Yes"))
#         )

# OLS
stargazer(mod1.ols, mod2.ols, mod3.ols, mod4.ols,
          omit=c("^factor.*", "^author.*"), 
          add.lines = list(
            c("Pair Fixed effects?", "No", "Yes", "Yes", "Yes"),
            c("Day Fixed effects?", "No", "No", "No", "Yes"),
            c("Author Fixed effects?", "No", "No", "No", "Yes")),
          type='html'
         )

# Poisson
stargazer(mod1.pois, mod2.pois, mod3.pois, mod4.pois,
          omit=c("^factor.*", "^author.*"), 
          add.lines = list(
            c("Pair Fixed effects?", "No", "Yes", "Yes", "Yes"),
            c("Day Fixed effects?", "No", "No", "No", "Yes"),
            c("Author Fixed effects?", "No", "No", "No", "Yes")),
          type='html'
         )

```

TODO: regression on secondary outcomes